Software architectures for workflow integration in science gateways

### 2016-04-20 paper.tex
Added a conclusion

Table~\ref{table:overall} provides an overall comparison between
architectures, based on the metrics in
Table~\ref{table:evaluation}. While Table~\ref{table:overall} provides
a global comparison between architectures, it should not be used
without the detailed metrics reported on Table~\ref{table:evaluation}
and discussed above. Overall, sub-tasking, and workflow import (with
service invocation) perform a bit better than tight integration,
service invocation and pool. Nested workflows stands a bit behind for
the reasons mentioned previously.
\begin{table*}
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Sub-task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Import} \\
  Integration effort (normalized total) & 
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99EF99}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E099}{0.44}
                                    & \cellcolor[HTML]{99BB99}{1.00}
                                      & \cellcolor[HTML]{99E899}{0.33}\\                           
Robustness (normalized total) & 
                                \cellcolor[HTML]{99F599}{0.14}
                                    & \cellcolor[HTML]{99E199}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99CE99}{0.71}
                                    & \cellcolor[HTML]{99BB99}{1.00}
                                    & \cellcolor[HTML]{99E199}{0.43}\\
  Extensibility (normalized total)  & \cellcolor[HTML]{99E099}{0.44}
                                     & \cellcolor[HTML]{99E099}{0.44}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99EF99}{0.22}
                                     & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99EF99}{0.22}\\
Scalability (normalized total)  & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}\\
Other features (normalized total) & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99EE99}\textbf{2.1}
                                    & \cellcolor[HTML]{99EE99}\textbf{2.1}
                                    & \cellcolor[HTML]{99FE99}\textbf{1.5}
                                    & \cellcolor[HTML]{99F499}\textbf{1.9}
                                    & \cellcolor[HTML]{99BB99}\textbf{4.0}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized total scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained by normalizing these scores
  as done in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}

@@

\todo{Section still to be written}

We abstracted architectures so that we can compare them using
objective metrics. We illustrated these architectural patterns on
examples of real systems.

What this work highlights and recommendations for science gateway
developers.

@@

\todo{Section still to be written}

\todo{FLI-IAM, Labex PRIMES, Ludmer Centre, whatever grant is funding
  POQ for integrating CBRAIN with PSOM.}

We warmly thank Rafael Ferreira da Silva for implementing the VIP
platform and creating Figure~\ref{fig:vip-architecture}.

>>>>

Table~\ref{table:overall} provides an overall comparison between
architectures, based on the metrics in
Table~\ref{table:evaluation}. While Table~\ref{table:overall} provides
a global comparison between architectures, it should not be used
without the detailed metrics reported on Table~\ref{table:evaluation}
and discussed above. Overall, sub-tasking, and workflow import (with
service invocation) perform a bit better than tight integration,
service invocation and pool. Nested workflows stands a bit behind for
the reasons mentioned previously.
\begin{table*}
\centering
\begin{tabular}{rcccccc}
                                    & \textbf{Tight}
                                    & \textbf{Service}
                                    & \textbf{Sub-task}
                                    & \textbf{Pool}
                                    & \textbf{Nested}
                                    & \textbf{Import} \\
  Integration effort (normalized total) & 
                                    \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99EF99}{0.22}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99E099}{0.44}
                                    & \cellcolor[HTML]{99BB99}{1.00}
                                      & \cellcolor[HTML]{99E899}{0.33}\\                           
Robustness (normalized total) & 
                                \cellcolor[HTML]{99F599}{0.14}
                                    & \cellcolor[HTML]{99E199}{0.43}
                                    & \cellcolor[HTML]{99FF99}{0.00}
                                    & \cellcolor[HTML]{99CE99}{0.71}
                                    & \cellcolor[HTML]{99BB99}{1.00}
                                    & \cellcolor[HTML]{99E199}{0.43}\\
  Extensibility (normalized total)  & \cellcolor[HTML]{99E099}{0.44}
                                     & \cellcolor[HTML]{99E099}{0.44}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99EF99}{0.22}
                                     & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99EF99}{0.22}\\
Scalability (normalized total)  & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}\\
Other features (normalized total) & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99BB99}{1.00}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99DD99}{0.50}
                                     & \cellcolor[HTML]{99FF99}{0.00}\\
                                    & \cellcolor[HTML]{99EE99}\textbf{2.1}
                                    & \cellcolor[HTML]{99EE99}\textbf{2.1}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}
                                    & \cellcolor[HTML]{99F499}\textbf{1.9}
                                    & \cellcolor[HTML]{99BB99}\textbf{4.0}
                                    & \cellcolor[HTML]{99FF99}\textbf{1.5}\\
\end{tabular}
\caption{Overall evaluation. Brighter colors and lower scores indicate better performance. Scores
  are obtained by summing the normalized total scores ($m'$ values) of
  each criterion in Table~\ref{table:evaluation} and the colors are obtained by normalizing these scores
  as done in Table~\ref{table:evaluation}. }
\label{table:overall}
\end{table*}

@@

% Summary of contributions
We reviewed architectures used to integration workflow engines in
science gateways, we described them in a system-independent framework
suitable for comparison, we illustrated them on real systems, we
developed quantitative metrics for evaluation, we evaluated these
metrics for all the architectures, and we discussed the pros and cons
of all the architectures based on these metrics.

% Impact of the work
To the best of our knowledge, our work is the first of its kind. Our
results can be used as recommendation for science gateway and workflow
engine developers to build new platforms, or to upgrade existing ones.

@@

We warmly thank Rafael Ferreira da Silva for its contribution to the
VIP platform and for creating Figure~\ref{fig:vip-architecture}. This
work is in the scope of the LABEX PRIMES (ANR-11- LABX-0063) of
Universit\'e de Lyon, within the program ``Investissements d’Avenir''
(ANR-11-IDEX-0007) operated by the French National Research Agency
(ANR). This work has been made possible with the support of the Irving
Ludmer Family Foundation and the Ludmer Centre for Neuroinformatics
and Mental Health.
